---
title: "Postratification Code"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Postratification code

We are looking into an MRP model for Counting Cockroaches and we want to learn what postratification is and if we can do it in our model.

The documents we study are currently together on a google doc

```{r}
library(tidyverse)



vote_yes <- c(rep(0, 25*(1-0.76)), 
              rep(1, 25*0.76),
              rep(0, 50*(1-0.3)),
              rep(1, 50*0.3))
vote_yes
mean(vote_yes)




```

That is our population. We will now make a sample with subgroups.

```{r}
poll_data <- tibble(
  group = c(rep("A", 25), rep("B", 10)),
  yes = c(rep(1, 19), rep(0, 6), rep(1, 3), rep(0, 7))
)
poll_data %>%
  group_by(group) %>%
  summarise(count = n())
```

Here are our subgroups and how many our represented in our sample. It does not match the proportions found in our population.

```{r}
Census <- tibble(
  group = c("A", "B"),
  pop = c(25, 50)
)
Census
mean(poll_data$yes)
```

Our mean for the sample varies from our population, so we stratify.

```{r}
group_support <- poll_data %>%
  group_by(group) %>%
  summarise(perc_support = mean(yes))
group_support

overall_support <- group_support %>%
  summarise(total_support = sum(perc_support * Census$pop/sum(Census$pop)))
overall_support
```

